Spectroscopic Characterization of New Er$^{3+}$ Host Crystals for Quantum Network Applications

### 2020-04-30 Draft.tex
Reformat thesis with report class

\documentclass[12pt]{puthesis}
%\documentclass[12pt,lot, lof, singlespace]{puthesis}
%\newcommand{\printmode}{}

% Front page materials
\title{Spectroscopic Characterization of New Er$^{3+}$ Host Crystals for Quantum Network Applications}
\submitted{May 2020}  
\copyrightyear{May 2020}  
\author{Henry Allen Ando}
\adviser{Professor Jeff D. Thompson}  
\department{Physics}

% Import packages
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{caption}
\usepackage[table,xcdraw]{xcolor}
\usepackage{tikz}
\usepackage{siunitx}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage[english]{babel}
\usepackage[autostyle, english = american]{csquotes}
\usepackage{siunitx}
\usepackage{float}
\usepackage{array}
\usepackage{paralist}
\usepackage{cite} 
\usepackage{multicol} 
\usepackage{wrapfig}
\usepackage{adjustbox}
\usepackage{physics}
\usepackage{rotating}
\setlength{\LTcapwidth}{\textwidth}

% Set page geometry options
\usepackage[colorlinks=true,linkcolor=black,citecolor=blue]{hyperref}
\usepackage[margin=1in]{geometry}
\setlength\parindent{28pt}
\usepackage{setspace}
\onehalfspacing

% Define functions
\newcommand{\erbium}[1][ ]{Er$^{3+}$#1}
\newcommand{\YSO}[1][ ]{Y$_{2}$SiO$_{5}$#1}
\newcommand{\ErYSO}[1][ ]{Er$^{3+}$:Y$_{2}$SiO$_{5}$#1}
\newcommand{\TiO}[1][ ]{TiO$_{2}$#1}
\newcommand{\supercite}[1]{$^{\text{\cite{#1}}}$}
\graphicspath{{Figures/}}
\newcommand{\notetoself}[1]{\textcolor{red}{#1}}
\newcommand{\wn}[1][ ]{cm$^{-1}$#1}

@@

% Printed vs. online formatting
\ifdefined\printmode
\usepackage{url}
\else
\ifdefined\proquestmode
\hypersetup{bookmarksnumbered}
\makeatletter
\hypersetup{pdftitle=\@title,pdfauthor=\@author}
\makeatother
\else
\hypersetup{colorlinks,bookmarksnumbered}
\makeatletter
\hypersetup{pdftitle=\@title,pdfauthor=\@author}
\makeatother
\fi % proquest or online formatting
\fi % printed or online formatting

% Enable or disable front matter
\ifodd 1
\renewcommand*{\makecopyrightpage}{}
\renewcommand*{\makeabstract}{}
% \renewcommand{\maketitlepage}{}
\else
\abstract{\input{abstract}}
\acknowledgements{\input{acknowledgements}}
\dedication{To my parents.}
\fi

@@

\begin{document}
\makefrontmatter

@@

\chapter{Introduction}
\section{A Brief History of Quantum Computing}
\label{sec:brief-hist-quant}

@@

% \notetoself{Here is a potential spot to talk about error correction. However, I'm not sure it's worth the space/time. For the moment, I'll leave only this reminder.}

@@

\item \listheader{Trapped ion quantum computers} use the electronic spins of ions trapped in an optical lattice as the qubit \cite{Cirac1995}. Alternatively, trapped neutral atoms can be used, with nuclear spins as the qubits \notetoself{[?]}. The dipole-dipole interactions between adjacent particles can be tuned to perform two-qubit gates, thus making atom trap quantum computers a viable platform for a universal quantum computer \notetoself{[?]}.

@@

\item \listheader{Point defects in solid state hosts} such as rare earth ions or nitrogen-vacancy (NV) centers in crystals are in some sense descendents of NMR-based quantum computing paradigms \notetoself{[?]}. In these systems, the spin states of valence electrons serve as qubits. Light-matter interfaces can be achieved by coupling these atoms with photons at the same energy as an optical transition in the qubit atom \notetoself{[?]}.

@@

\begin{figure}[b]
  \centering
  \includegraphics[width=0.8\textwidth]{Nanophotonics}
  \caption{A lensed fiber couples into a silicon photonic cavity stamped on top of an \erbium[]-doped \YSO crystal. Red arrows represent the spins of \erbium ions in the crystal substrate. Figure from \cite{Dibos2018}.}
  \label{fig:cavity}
\end{figure}

@@

\begin{wrapfigure}{r}{0.5\textwidth}
  \centering
  \includegraphics[width=0.48\textwidth]{EnergyLevelDiagram}
  \caption{Diagram showing the Stark splitting due to electric fields within the crystal (blue) and the Zeeman splitting in an applied magnetic field (green). The transition between the lowest ground and excited state levels, labelled in red, typically falls around 1530 nm.}
  \label{fig:energyleveldiagram}
\end{wrapfigure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.9\textwidth]{PLESetupDiagram.pdf}
  \caption{Schematic of our spectroscopy experiment. A half-wave plate is marked in blue, and a dichroic mirror is marked in green. }
  \label{fig:ple}
\end{figure}

Our PLE setup is shown in Figure \ref{fig:ple}. A tunable diode laser is amplified by an erbium-doped fiber amplifier up to \notetoself{200 mW?}. The laser is then passed through a chopper. A half-wave plate (blue) at the output of the fiber enables coarse control over the polarization of the laser before it passes through a polarizing beamsplitter. A photodiode measures the light rejected by the PBS, informing the rotation of the HWP. The laser then passes through a beam expander consisting of two lenses, before reflecting off a PBS towards the vapor cryostat containing the sample. Before the cryostat the laser passes through a lens which focuses it onto the sample surface. A camera, which is added to the beam path with a dichroic (green), helps aim the laser at the sample.

@@

\begin{figure}[b]
  \centering
  \includegraphics[width=0.47\textwidth]{PeakFinding}
  \hfill
  \includegraphics[width=0.47\textwidth]{LineSorting}
  \caption{Left: a screenshot of peak sorting. Red dots are all potential peaks, green dots are the ones that have been manually selected as belonging to physical features. Right: a screenshot of grouping excitation lines into different sites. In the given figure, all lines belong to the same site.}
  \label{fig:manual}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[scale=1]{JinD_spectrum_13K}
  \caption{Excitation-emission spectrum of MgO at 13K.}
  \label{fig:mgospectrum}
\end{figure}

\subsection{Sample preparation}
Implanted with $10^{19}$ dose \notetoself{find out units on this}. Unannealed.

@@

\begin{wrapfigure}{r}{0.5\textwidth}
  \centering
  \includegraphics[width=0.48\textwidth]{Site2Multiplicity}
  \caption{Detail plot of Site 2 side bands in the MgO excitation-emission spectrum at 13K.}
  \label{fig:site2sidebands}
\end{wrapfigure}

@@

\begin{figure}[b]
  \centering
  \includegraphics[width=0.48\textwidth]{Site3_y1}
  \includegraphics[width=0.48\textwidth]{Site3_y2}
  \caption{Excitation peaks at $Z_1Y_1$ (left) and $Z_1Y_2$ (right) in Site 3. The intensity profile discussed in Equation \eqref{eq:1} is fitted to the $Z_{1}Y_{2}$ data. Fitted model parameters are: $a_{1} = 2.3$, $\Delta_{1} = 0.05$, $\Gamma_{1} = 0.28$, $a_{2} = 1.6$, $\Delta_{2} = -0.05$, $\Gamma_{2} = 0.28$, $\Gamma_{3} = 0.0025$, $b = 0.12$}
  \label{fig:site3peaks}
\end{figure}

@@

\begin{figure}[b]
  \centering
  \includegraphics[scale=0.97]{JinD_site1_13K}\hfill
  \includegraphics[scale=0.97]{JinD_site1_32K}\\
  \includegraphics[scale=0.97]{JinD_site1_60K}\hfill
  \includegraphics[scale=0.97]{JinD_site1_106K}
  \caption{Transition assignments for excitation-emission spectra of MgO for Site 1 at 13, 32, 60, and 106K respectively. All observed peaks are marked. Green lines correspond to excitation (emission) from $Z_{1}$ ($Y_{1}$), magenta lines correspond to origin states that thermally occupy at higher temperatures.}
  \label{fig:mgosite1}
\end{figure}

\begin{figure}[b]
  \centering
  \includegraphics[scale=0.97]{JinD_site2_13K}\hfill
  \includegraphics[scale=0.97]{JinD_site2_32K}\\
  \includegraphics[scale=0.97]{JinD_site2_60K}\hfill
  \includegraphics[scale=0.97]{JinD_site2_106K}
  \caption{Transition assignments for excitation-emission spectra of MgO for Site 2 at 13, 32, 60, and 106K respectively. All observed peaks are marked. Green lines correspond to excitation (emission) from $Z_{1}$ ($Y_{1}$), magenta lines correspond to origin states that thermally occupy at higher temperatures.}
  \label{fig:mgosite2}
\end{figure}

\begin{figure}[b]
  \centering
  \includegraphics[scale=0.97]{JinD_site3_13K}\hfill
  \includegraphics[scale=0.97]{JinD_site3_32K}\\
  \includegraphics[scale=0.97]{JinD_site3_60K}\hfill
  \includegraphics[scale=0.97]{JinD_site3_106K}
  \caption{Transition assignments for excitation-emission spectra of MgO for Site 3 at 13, 32, 60, and 106K respectively. All observed peaks are marked. Green lines correspond to excitation (emission) from $Z_{1}$ ($Y_{1}$), magenta lines correspond to origin states that thermally occupy at higher temperatures. Emission lines for which no level assignment can be determined are plotted in yellow.}
  \label{fig:mgosite3}
\end{figure}

\begin{figure}[b]
  \centering
  \includegraphics[scale=0.97]{JinD_site4_13K}\hfill
  \includegraphics[scale=0.97]{JinD_site4_32K}\\
  \includegraphics[scale=0.97]{JinD_site4_60K}\hfill
  \includegraphics[scale=0.97]{JinD_site4_106K}
  \caption{Transition assignments for excitation-emission spectra of MgO for Site 4 at 13, 32, 60, and 106K respectively. No data exists for $Z_{1}Y_{1}$ at 13K, so this line is dotted in that figure. All observed peaks are marked. Green lines correspond to excitation (emission) from $Z_{1}$ ($Y_{1}$), magenta lines correspond to origin states that thermally occupy at higher temperatures.}
  \label{fig:mgosite4}
\end{figure}

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.75]{JinD_site1_temp}
  \includegraphics[scale=0.75]{JinD_site2_temp}
  \includegraphics[scale=0.75]{JinD_site3_temp}
  \includegraphics[scale=0.75]{JinD_site4_temp}
  \caption{Temperature dependence of emission spectrum in MgO, excited at $Z_{1}Y_{1}$, for Sites 1, 2, 3, and 4, from top to bottom. Each peak is labeled with its corresponding emission transition.}
  \label{fig:mgotemp}
\end{figure}

@@

The array-detector-based emission spectrometer greatly sped up the acquisition of excitation-emission spectra. However, it has two primary limitations which impose constraints on our measurements. One is the resolution. The detector has \notetoself{1024} bins, which sets the resolution on a 100 nm wide scan to only 0.1 nm, which is often not enough for our purposes. Furthermore, increasing the resolution by decreasing the width of the slit attenuates the signal, further lowering the signal to noise ratio.

@@

\begin{wrapfigure}{r}{0.3\textwidth}
  \centering
  \includegraphics[width=0.23\textwidth]{FTIRMainIdea}
  \caption{A Fourier transform spectrometer.}
  \label{fig:ftirmainidea}
\end{wrapfigure}

@@

\begin{figure}[b]
  \centering
  \includegraphics[width=\textwidth]{FTIRSetupDiagram}
  \caption{The optical design of our FTIR spectrometry setup. 1400 nm long-pass filters are marked in blue. A removable mirror is marked by a dotted line; when the mirror is taken out, the beams travel 3 meters to an alignment mark in the far field. }
  \label{fig:ftirdiagram}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[scale=1]{RawRefSignal}
  \caption{Raw data (black) from the reference PD, taken from the center of the scan when the mirror is moving fastest. The mean of the data has been subtracted for clarity, and a cosine has been fitted to the data (red dotted line). The frequency of the fitted cosine is a factor of 0.85 below the Nyquist frequency.}
  \label{fig:reference}
\end{figure}

@@

\begin{wrapfigure}{r}{3.2in}
  \centering
  \includegraphics[scale=1]{Speed}
  \caption{Mirror displacements versus time at 0.5 Hz for two complete scans (one in each direction), with a fitted cosine.}
  \label{fig:speed}
\end{wrapfigure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[scale=1]{EmissionResolution}
  \caption{Emission spectra of the Toptica bleedthrough at four different excitation points (selected for having no fluourescence) in an MgO excitation-emission spectrum recorded using the array detector. Data (black) have been fitted with Gaussian curves (red dotted lines), and the widths of the Gaussians extracted. The average width is $1.08\pm 0.04$ \wn[.]}
  \label{fig:emresolution}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.43\textwidth]{NewMirrorScheme}
  \caption{A new corner cube mirror scheme to double the effective resolution of the spectrometer. The corner cube is being viewed head on from the perspective of the beamsplitter. The beam enters at point 1, and exits the mobile corner cube (purple) at point 2. It is then reflected off a second, stationary corner cube (orange) which faces the mobile corner cube, and is rotated so that the beam only reflects off two of the faces. The beam then reenters the mobile corner cube at point 3, and exits at point 4. It then reflects off a D-shaped mirror (mint) and returns to the beamsplitter along the same path, passing through points 4, 3, 2, and finally 1.}
  \label{fig:newmirrorscheme}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[height=2.5in]{LEDsignal}
  \includegraphics[height=2.5in]{LEDspectrumzoom}
  \includegraphics[height=2.5in]{LEDspectrum}
  \caption{Top left: raw infrared photodiode signal for the broad spectrum LED. Bottom: complete power spectrum for the broad spectrum LED. Top right: detail plot of the boxed region in the bottom figure.}
  \label{fig:LED}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics{TOPspectrum}
  \caption{Detail plot of the only feature in the FTIR frequency spectrum of the Toptica diode laser outputting 26 $\mu$W at 6531.7 \wn[]. A Gaussian has been fitted to the peak, yielding a FWHM of $2.39 \pm 0.17$ \wn and a central frequency of $6531.7 \pm 0.2$ \wn[.] The signal to noise ratio of this signal is approximately $6.4\times 10^{9}$.}
  \label{fig:toptica}
\end{figure}

@@

\singlespacing
\bibliographystyle{prsty}
\cleardoublepage
\ifdefined\phantomsection
  \phantomsection  % makes hyperref recognize this section properly for pdf link
\else
\fi
\addcontentsline{toc}{chapter}{Bibliography}
\bibliography{thesis}

>>>>

\documentclass[12pt]{report}
%\documentclass[12pt,lot, lof, singlespace]{puthesis}
%\newcommand{\printmode}{}

% Import packages
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{caption}
\usepackage[table,xcdraw]{xcolor}
\usepackage{tikz}
\usepackage{siunitx}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage[english]{babel}
\usepackage[autostyle, english = american]{csquotes}
\usepackage{siunitx}
\usepackage{float}
\usepackage{array}
\usepackage{paralist}
\usepackage{cite} 
\usepackage{multicol} 
\usepackage{wrapfig}
\usepackage{adjustbox}
\usepackage{physics}
\usepackage{rotating}
\usepackage{etoolbox}
\usepackage{changepage}
\setlength{\LTcapwidth}{\textwidth}

% Set page geometry options
\usepackage[colorlinks=true,linkcolor=black,citecolor=blue]{hyperref}
\usepackage[margin=1in]{geometry}
\setlength\parindent{28pt}
\usepackage{setspace}
\doublespacing

% Produce images?
\newtoggle{imgs}
% \toggletrue{imgs}
\togglefalse{imgs}

% Define the content to go in the header
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{}
\fancyhead[RO,LE]{\nouppercase{\rightmark}} % section number + title
% \fancyfoot{}
% \fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}

% Define functions
\newcommand{\erbium}[1][ ]{Er$^{3+}$#1}
\newcommand{\YSO}[1][ ]{Y$_{2}$SiO$_{5}$#1}
\newcommand{\ErYSO}[1][ ]{Er$^{3+}$:Y$_{2}$SiO$_{5}$#1}
\newcommand{\TiO}[1][ ]{TiO$_{2}$#1}
\newcommand{\supercite}[1]{$^{\text{\cite{#1}}}$}
\graphicspath{{Figures/}}
\newcommand{\notetoself}[1]{\textcolor{red}{#1}}
\newcommand{\wn}[1][ ]{cm$^{-1}$#1}
\renewcommand{\bibname}{References}

@@

@@

\begin{document}

\pagenumbering{roman}
\setcounter{page}{1}

\begin{titlepage}
  \singlespacing
  \begin{center}
    \vspace*{5mm}
    \Large{\textbf{Spectroscopic Characterization of New \erbium Host Crystals for Quantum Network Applications}}

    \vspace{0.5cm}

    \Large{Henry Ando}

    \vfill
    \includegraphics[height=2in]{Figures/Princeton.png}
    \vfill

    \normalsize{A thesis presented in partial fulfillment of the\\requirements for the degree of Bachelor of Arts (A.B.).}

    \vspace{0.8cm}

    \normalsize{Advised by Professor Jeff D. Thompson} \\
    \normalsize{Second Reader: Professor Waseem Bakr}

    \vspace{0.8cm}

    \normalsize{Department of Physics\\
      Princeton University\\
      Princeton, NJ\\
      2019-2020}
  \end{center}
\end{titlepage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\thispagestyle{empty}
\vspace*{1in}
\begin{flushright}
  To my family and friends.
\end{flushright}
\clearpage
\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\thispagestyle{empty}
\addcontentsline{toc}{chapter}{Abstract}
\onehalfspacing
\vspace*{1cm}
\begin{center}
  \textbf{Abstract}
\end{center}
  \noindent Large-scale quantum networks will require reliable single-photon sources for distributing entanglement over long distances. The \erbium ion is a good candidate for this purpose as it has an optically accessible transition at 1550 nm, the so-called ``telecom'' wavelength at which light propagates through optical fibers with minimal loss. However, this transition is electric-dipole forbidden and thus spontaneous emission from it is slow (around 100 Hz).
  Such a bandwidth constraint would be crippling in a real photonic quantum system. Previously, the Thompson lab has doped \erbium ions into \YSO and coupled them to silicon nanophotonic cavities, enabling the observation of single ions and enhancing the spontaneous emission rate by a factor of 600 through the Purcell effect \cite{Dibos2018}.
  However, the bulk-doped \ErYSO system has two flaws. One is that \YSO has strong nuclear spins which limit the  $T_{1}$ and $T_{2}$ spin coherence times of the \erbium ions. The other is that the lower bound on the density of \erbium possible through the bulk-doping process is still too high for individual \erbium ions to be addressed optically.
  These issues have motivated a search for new host crystals which can be doped with \erbium through ion implantation, hopefully resulting in substantially lower concentrations of \erbium ions than would be possible through bulk doping. In this work, we characterize the spectral properties of \erbium implanted in a promising new host crystal, and discuss new techniques for improving the resolution of future such measurements.

\vspace*{\fill}
\begin{center}
  This paper represents my own work in accordance with University regulations.\\
  \includegraphics[width=2in]{Signature}
\end{center}
\vspace*{\fill}
\clearpage
\newpage
\doublespacing
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\tableofcontents

@@

\chapter{Introduction}
\pagenumbering{arabic}
\setcounter{page}{1}
\section{A Brief History of Quantum Computing}
\label{sec:brief-hist-quant}

@@

@@

\item \listheader{Trapped ion quantum computers} use the electronic spins of ions trapped in an optical lattice as the qubit \cite{Cirac1995}. Alternatively, trapped neutral atoms can be used, with nuclear spins as the qubits \cite{Saskin2019}. The dipole-dipole interactions between adjacent particles can be tuned to perform two-qubit gates, thus making atom trap quantum computers a viable platform for a universal quantum computer.

@@

\item \listheader{Point defects in solid state hosts} such as rare earth ions or nitrogen-vacancy (NV) centers in crystals are in some sense descendents of NMR-based quantum computing paradigms \cite{Rose2018,Zhong2015}. In these systems, the spin states of valence electrons serve as qubits. Light-matter interfaces can be achieved by coupling these atoms with photons at the same energy as an optical transition in the qubit atom \cite{Togan2010,Bernien2013,Greve2012}.

@@

\begin{figure}[b]
  \centering
  \iftoggle{imgs}{
    \includegraphics[width=0.8\textwidth]{Nanophotonics}
  }{}
  \caption{A lensed fiber couples into a silicon photonic cavity stamped on top of an \erbium[]-doped \YSO crystal. Red arrows represent the spins of \erbium ions in the crystal substrate. Figure from \cite{Dibos2018}.}
  \label{fig:cavity}
\end{figure}

@@

\begin{wrapfigure}{r}{0.5\textwidth}
  \centering
  \iftoggle{imgs}{
    \includegraphics[width=0.48\textwidth]{EnergyLevelDiagram}
  }{}
  \caption{Diagram showing the Stark splitting due to electric fields within the crystal (blue) and the Zeeman splitting in an applied magnetic field (green). The transition between the lowest ground and excited state levels, labelled in red, typically falls around 1530 nm.}
  \label{fig:energyleveldiagram}
\end{wrapfigure}

@@

\begin{figure}[t]
  \centering
  \iftoggle{imgs}{
    \includegraphics[width=0.9\textwidth]{PLESetupDiagram.pdf}
  }{}
  \caption{Schematic of our spectroscopy experiment. A half-wave plate is marked in blue, and a dichroic mirror is marked in green. }
  \label{fig:ple}
\end{figure}

Our PLE setup is shown in Figure \ref{fig:ple}. A tunable diode laser is amplified by an erbium-doped fiber amplifier up to 200 mW. The laser is then passed through a chopper. A half-wave plate (blue) at the output of the fiber enables coarse control over the polarization of the laser before it passes through a polarizing beamsplitter. A photodiode measures the light rejected by the PBS, informing the rotation of the HWP. The laser then passes through a beam expander consisting of two lenses, before reflecting off a PBS towards the vapor cryostat containing the sample. Before the cryostat the laser passes through a lens which focuses it onto the sample surface. A camera, which is added to the beam path with a dichroic (green), helps aim the laser at the sample.

@@

\begin{figure}[b]
  \centering
  \iftoggle{imgs}{
    \includegraphics[width=0.47\textwidth]{PeakFinding}
    \hfill
    \includegraphics[width=0.47\textwidth]{LineSorting}
  }{}
  \caption{Left: a screenshot of peak sorting. Red dots are all potential peaks, green dots are the ones that have been manually selected as belonging to physical features. Right: a screenshot of grouping excitation lines into different sites. In the given figure, all lines belong to the same site.}
  \label{fig:manual}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \iftoggle{imgs}{
    \includegraphics[scale=1]{JinD_spectrum_13K}
  }
  \caption{Excitation-emission spectrum of MgO at 13K.}
  \label{fig:mgospectrum}
\end{figure}

\subsection{Sample preparation}
Implanted with $10^{19}$ ion dose. Unannealed.

@@

\begin{wrapfigure}{r}{0.5\textwidth}
  \centering
  \iftoggle{imgs}{
    \includegraphics[width=0.48\textwidth]{Site2Multiplicity}
  }{}
  \caption{Detail plot of Site 2 side bands in the MgO excitation-emission spectrum at 13K.}
  \label{fig:site2sidebands}
\end{wrapfigure}

@@

\begin{figure}[b]
  \centering
  \iftoggle{imgs}{
    \includegraphics[width=0.48\textwidth]{Site3_y1}
    \includegraphics[width=0.48\textwidth]{Site3_y2}
  }{}
  \caption{Excitation peaks at $Z_1Y_1$ (left) and $Z_1Y_2$ (right) in Site 3. The intensity profile discussed in Equation \eqref{eq:1} is fitted to the $Z_{1}Y_{2}$ data. Fitted model parameters are: $a_{1} = 2.3$, $\Delta_{1} = 0.05$, $\Gamma_{1} = 0.28$, $a_{2} = 1.6$, $\Delta_{2} = -0.05$, $\Gamma_{2} = 0.28$, $\Gamma_{3} = 0.0025$, $b = 0.12$}
  \label{fig:site3peaks}
\end{figure}

@@

\begin{figure}[b]
  \centering
  \iftoggle{imgs}{
    \includegraphics[scale=0.97]{JinD_site1_13K}\hfill
    \includegraphics[scale=0.97]{JinD_site1_32K}\\
    \includegraphics[scale=0.97]{JinD_site1_60K}\hfill
    \includegraphics[scale=0.97]{JinD_site1_106K}
  }{}
  \caption{Transition assignments for excitation-emission spectra of MgO for Site 1 at 13, 32, 60, and 106K respectively. All observed peaks are marked. Green lines correspond to excitation (emission) from $Z_{1}$ ($Y_{1}$), magenta lines correspond to origin states that thermally occupy at higher temperatures.}
  \label{fig:mgosite1}
\end{figure}

\begin{figure}[b]
  \centering
  \iftoggle{imgs}{
    \includegraphics[scale=0.97]{JinD_site2_13K}\hfill
    \includegraphics[scale=0.97]{JinD_site2_32K}\\
    \includegraphics[scale=0.97]{JinD_site2_60K}\hfill
    \includegraphics[scale=0.97]{JinD_site2_106K}
  }{}
  \caption{Transition assignments for excitation-emission spectra of MgO for Site 2 at 13, 32, 60, and 106K respectively. All observed peaks are marked. Green lines correspond to excitation (emission) from $Z_{1}$ ($Y_{1}$), magenta lines correspond to origin states that thermally occupy at higher temperatures.}
  \label{fig:mgosite2}
\end{figure}

\begin{figure}[b]
  \centering
  \iftoggle{imgs}{
    \includegraphics[scale=0.97]{JinD_site3_13K}\hfill
    \includegraphics[scale=0.97]{JinD_site3_32K}\\
    \includegraphics[scale=0.97]{JinD_site3_60K}\hfill
    \includegraphics[scale=0.97]{JinD_site3_106K}
  }{}
  \caption{Transition assignments for excitation-emission spectra of MgO for Site 3 at 13, 32, 60, and 106K respectively. All observed peaks are marked. Green lines correspond to excitation (emission) from $Z_{1}$ ($Y_{1}$), magenta lines correspond to origin states that thermally occupy at higher temperatures. Emission lines for which no level assignment can be determined are plotted in yellow.}
  \label{fig:mgosite3}
\end{figure}

\begin{figure}[b]
  \centering
  \iftoggle{imgs}{
  \includegraphics[scale=0.97]{JinD_site4_13K}\hfill
  \includegraphics[scale=0.97]{JinD_site4_32K}\\
  \includegraphics[scale=0.97]{JinD_site4_60K}\hfill
  \includegraphics[scale=0.97]{JinD_site4_106K}
  }{}
  \caption{Transition assignments for excitation-emission spectra of MgO for Site 4 at 13, 32, 60, and 106K respectively. No data exists for $Z_{1}Y_{1}$ at 13K, so this line is dotted in that figure. All observed peaks are marked. Green lines correspond to excitation (emission) from $Z_{1}$ ($Y_{1}$), magenta lines correspond to origin states that thermally occupy at higher temperatures.}
  \label{fig:mgosite4}
\end{figure}

\begin{figure}[t]
  \centering
  \iftoggle{imgs}{
    \includegraphics[scale=0.75]{JinD_site1_temp}
    \includegraphics[scale=0.75]{JinD_site2_temp}
    \includegraphics[scale=0.75]{JinD_site3_temp}
    \includegraphics[scale=0.75]{JinD_site4_temp}
  }{}
  \caption{Temperature dependence of emission spectrum in MgO, excited at $Z_{1}Y_{1}$, for Sites 1, 2, 3, and 4, from top to bottom. Each peak is labeled with its corresponding emission transition.}
  \label{fig:mgotemp}
\end{figure}

@@

The array-detector-based emission spectrometer greatly sped up the acquisition of excitation-emission spectra. However, it has two primary limitations which impose constraints on our measurements. One is the resolution. The detector has 1024 bins, which sets the resolution on a 100 nm wide scan to only 0.1 nm, which is often not enough for our purposes. Furthermore, increasing the resolution by decreasing the width of the slit attenuates the signal, further lowering the signal to noise ratio.

@@

\begin{wrapfigure}{r}{0.3\textwidth}
  \centering
  \iftoggle{imgs}{
    \includegraphics[width=0.23\textwidth]{FTIRMainIdea}
  }{}
  \caption{A Fourier transform spectrometer.}
  \label{fig:ftirmainidea}
\end{wrapfigure}

@@

\begin{figure}[b]
  \centering
  \iftoggle{imgs}{
    \includegraphics[width=\textwidth]{FTIRSetupDiagram}
  }{}
  \caption{The optical design of our FTIR spectrometry setup. 1400 nm long-pass filters are marked in blue. A removable mirror is marked by a dotted line; when the mirror is taken out, the beams travel 3 meters to an alignment mark in the far field. }
  \label{fig:ftirdiagram}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \iftoggle{imgs}{
    \includegraphics[scale=1]{RawRefSignal}
  }{}
  \caption{Raw data (black) from the reference PD, taken from the center of the scan when the mirror is moving fastest. The mean of the data has been subtracted for clarity, and a cosine has been fitted to the data (red dotted line). The frequency of the fitted cosine is a factor of 0.85 below the Nyquist frequency.}
  \label{fig:reference}
\end{figure}

@@

\begin{wrapfigure}{r}{3.2in}
  \centering
  \iftoggle{imgs}{
    \includegraphics[scale=1]{Speed}
  }{}
  \caption{Mirror displacements versus time at 0.5 Hz for two complete scans (one in each direction), with a fitted cosine.}
  \label{fig:speed}
\end{wrapfigure}

@@

\begin{figure}[t]
  \centering
  \iftoggle{imgs}{
    \includegraphics[scale=1]{EmissionResolution}
  }{}
  \caption{Emission spectra of the Toptica bleedthrough at four different excitation points (selected for having no fluourescence) in an MgO excitation-emission spectrum recorded using the array detector. Data (black) have been fitted with Gaussian curves (red dotted lines), and the widths of the Gaussians extracted. The average width is $1.08\pm 0.04$ \wn[.]}
  \label{fig:emresolution}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \iftoggle{imgs}{
    \includegraphics[width=0.43\textwidth]{NewMirrorScheme}
  }{}
  \caption{A new corner cube mirror scheme to double the effective resolution of the spectrometer. The corner cube is being viewed head on from the perspective of the beamsplitter. The beam enters at point 1, and exits the mobile corner cube (purple) at point 2. It is then reflected off a second, stationary corner cube (orange) which faces the mobile corner cube, and is rotated so that the beam only reflects off two of the faces. The beam then reenters the mobile corner cube at point 3, and exits at point 4. It then reflects off a D-shaped mirror (mint) and returns to the beamsplitter along the same path, passing through points 4, 3, 2, and finally 1.}
  \label{fig:newmirrorscheme}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \iftoggle{imgs}{
    \includegraphics[height=2.5in]{LEDsignal}
    \includegraphics[height=2.5in]{LEDspectrumzoom}
    \includegraphics[height=2.5in]{LEDspectrum}
  }{}
  \caption{Top left: raw infrared photodiode signal for the broad spectrum LED. Bottom: complete power spectrum for the broad spectrum LED. Top right: detail plot of the boxed region in the bottom figure.}
  \label{fig:LED}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \iftoggle{imgs}{
    \includegraphics{TOPspectrum}
  }{}
  \caption{Detail plot of the only feature in the FTIR frequency spectrum of the Toptica diode laser outputting 26 $\mu$W at 6531.7 \wn[]. A Gaussian has been fitted to the peak, yielding a FWHM of $2.39 \pm 0.17$ \wn and a central frequency of $6531.7 \pm 0.2$ \wn[.] The signal to noise ratio of this signal is approximately $6.4\times 10^{9}$.}
  \label{fig:toptica}
\end{figure}

@@

In this work, we have presented the current status of the spectroscopic characterization of MgO, a promising new host crystal for implanted \erbium ions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\renewcommand{\bibname}{References}
\singlespacing
\bibliographystyle{prsty}
\cleardoublepage
\ifdefined\phantomsection
  \phantomsection  % makes hyperref recognize this section properly for pdf link
\else
\fi
\addcontentsline{toc}{chapter}{References}
\bibliography{thesis}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\addcontentsline{toc}{chapter}{Acknowledgements}
\chapter*{Acknowledgements}
